A Data-Driven Framework for Neural Field Modelling

### 2010-10-31 ltx/first_order_framework/LaTeX_Manuscript.tex
changes to state and parameter estimates

Histograms of the parameter estimates obtained over the 100 realisations are shown in Figure~\ref{fig:Figure7}. The actual parameter values, the mean estimates, corresponding standard deviations and biases are given in Table~\ref{tab:Parameters estimates}. The biases show the percentage differences between the actual values and the mean parameter estimates. The mean estimates are in good agreement with the actual values.

The reconstructed connectivity kernels from the estimated parameters are shown in Figure~\ref{fig:Figure8}, where the mean over the 100 realisations is shown as a dotted line and the 95\% confidence interval is indicated by the grey shaded region. The figure verifies that the shape of the estimated connectivity kernel is in good accordance with the true kernel. The true kernel lies within the confidence interval; however, the mean estimated kernel is more negative than the actual kernel due to the small bias in the estimates of the inhibitory parameter, $\hat\theta_1$, as seen in Figure~\ref{fig:Figure7}(C).

The accuracy of the state estimates was evaluated by comparing the field reconstruction to the true field using the mean (over iterations) of the root mean square error (MRMSE) over space. The MRMSE of the field estimates over time for 100 realisations is shown in Figure~\ref{fig:Figure9}, with the $95~\%$ confidence interval. At each time point, the error is consistently around 0.5~mV, which is approximately 7.1~\% of the field voltage range ([-3.29,3.77]~mV). The error in the reconstructed field is mostly due to the loss of high spatial frequency information from the basis function decomposition as illustrated in Figure~\ref{fig:Figure10}. The figure shows a snapshot at a single time instant of the true neural field, the estimated field and the corresponding error, which is the difference between the true and estimated neural fields. It can be seen in Figure~\ref{fig:Figure10}(B) that the estimated field contains the basic structure of the true field (shown in Figure~\ref{fig:Figure10}(A)), but is missing the higher-frequency detail.

>>>>

Histograms of the parameter estimates obtained over the 100 realisations are shown in Figure~\ref{fig:Figure7}. The actual parameter values, the mean estimates, corresponding standard deviations and biases are given in Table~\ref{tab:Parameters estimates}. The biases show the percentage differences between the actual values and the mean parameter estimates. \parham{The mean estimates are in good agreement with the actual values of the connectivity kernel parameters, however $\xi$ is outside the estimate distribution.}

The accuracy of the state estimates was evaluated by comparing the field reconstruction to the true field using the mean (over iterations) of the root mean square error (MRMSE) over space. The MRMSE of the field estimates over time for 150 realisations is shown in Figure~\ref{fig:Figure9}, with the $95~\%$ confidence interval. At each time point, the error is consistently around 0.5~mV, which is approximately 7.1~\% of the field voltage range ([-3.29,3.77]~mV). The error in the reconstructed field is mostly due to the loss of high spatial frequency information from the basis function decomposition as illustrated in Figure~\ref{fig:Figure10}. The figure shows a snapshot at a single time instant of the true neural field, the estimated field and the corresponding error, which is the difference between the true and estimated neural fields. It can be seen in Figure~\ref{fig:Figure10}(B) that the estimated field contains the basic structure of the true field (shown in Figure~\ref{fig:Figure10}(A)), but is missing the higher-frequency detail.

\parham{To further study the ability of the proposed technique we used differents sets of connectivity basis functions parameters. The reconstructed connectivity kernels from the estimated parameters are shown in Figure~\ref{fig:Figure8}, where for each subset the mean over the 50 realisations is shown as a dotted line and the 95\% confidence interval is indicated by the grey shaded region.} \parham{this bit should change as well:} The figure verifies that the shape of the estimated connectivity kernel is in good accordance with the true kernel. The true kernel lies within the confidence interval; however, the mean estimated kernel is more negative than the actual kernel due to the small bias in the estimates of the inhibitory parameter, $\hat\theta_1$, as seen in Figure~\ref{fig:Figure7}(C).
